---
title: "CourseSummary"
author: "Lori Shepherd"
date: "October 21, 2016"
output: html_document
---

## Day 1: Packages & Version Control 

We learned to create a package using [devtools][1]. The way to get started is to 
create a skeleton of a package. 

```
library(devtools)
create()
```
This creates a directory with a couple files and a folder. 
We then did the following 

1. The DESCRIPTION contains intfo about the package; we edited it for our 
    purposes. 
2. We looked at the NAMESPACE but didn't touch it 
3. We created our first function in the R folder, `hi()`

We then used [roxygen2][2] to add 
documentation to the function, including info about parameters and return 
values. We also used tag (`@export`) to indicate that we wanted to export the 
function in the namespace. 

We managed source code using [GitHub][3]. 

```{r our-package}
library(LorisWorld)
hi("Brad")
hi("Have a Headache","whisper")
hi("Hard of hearing", "shout")
```

## Day 2: Classic, Rich, and Tidy Data

'Classic' data is represented as a `data.frame()` with samples as rows and 
features as columns. 

```{r}
pheno = "~/a/randomProjects/workshop/LorisWorld/ALL-phenoData.csv"
exprs = "~/a/randomProjects/workshop/LorisWorld/ALL-expression.csv"
classic = input_classic(pheno, exprs)
classic[1:5,c(1:3,22:24)]
```

One of the things we did was plot the distribution of expression values across
genes. 

```{r classic-exprs-hit}
hist(colMeans(classic[,-(1:22)]))
```

[1]: https://cran.r-project.org/web/packages/devtools/index.html
[2]: https://cran.r-project.org/package=roxygen2
[3]: https://github.com
